%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.


\indent I would like to thank my committee members, Dr. Burgess, Dr. Segal, and Dr. Threadgill, for their insight and guidance throughout the course of my doctoral research training. A special thank you goes to Dr. Jane Welsh for her support, constant encouragement and motivation, all of which are immeasurable.

I must also thank my program faculty and staff for their assistance. I will miss the familiarity of seeing Ms. Julia in her office. Additionally, I want to give thanks to the Department of Biochemistry and the Department of Veterinary Pathobiology staff for always greeting me with a welcoming smile. Finally, the Texas A\&M University Interdisciplinary Genetics Program and the Texas A\&M University College of Veterinary Medicine \& Biomedical Sciences, Department of Veterinary Pathobiology were instrumental in supporting my research pursuits.

I would like to recognize:
Mrs. Shrock my first grade teacher who managed to inscribe a love of reading, which managed to survive despite racist teachers actively working to tear me down a few years later.
Ms. Jocelyn Sisson my tenth grade English teacher who gave me a backbone and didn't let me settle for anything less than perfection.
Dr. Bilal M. M. Bomani for teaching me the importance of networking and interpersonal relationships.
Dr. Danny Alge for teaching me the scientific method.
And Dr. James Cooper for teaching me how to design and execute experiments.

I want to thank Dr. William Griffith and Ms. Annette Fincher, who took time out of their busy schedules to teach me electrophysology despite it not making it into this body of work.

An immense thanks go to my fellow graduate students, colleagues and lab members: Dr. Sarah Black Christian, Dr. Cole McQueen, Dr. Paul R. Hillman, and Ms. Hillary Shaheen. Thank you all for your assistance.
A special thank you goes to the Genetics Graduate Student Society for being an open place to talk with many late nights, free food, and much needed laughter. I wouldn't have been able to get through this without the camaraderie.

Finally, I cannot thank my family enough for their love and support.
To my supportive family, my many aunts, uncles, and cousins who always asked about my research, I cannot thank you enough for the large amount of love and constant encouragement you all sent my way. I'd thank you each individually, but then I'd run over my page limit.
To my little brother Victor and little sister Izzy, who understand the numerous holidays and birthdays I had to miss because of this work.
To my older sister Tasha, who's support and understanding was unmeasurable.
To my other brother Joshua, who was always in my corner and to this day is still my greatest hero.
To my twin, Erica, for always lending an ear and wanting to fight for me at every turn during this difficult and trying process.
To my father who will likely be the first to read this in it's entirety.
And most importantly, to my beautiful, powerful, passionate mother whose life embodied Faith. She believed in all of her children with all of her heart to her very last breath. It is thanks to my mother and god that I am here today, and I could not thank her enough. Thank you mom, for everything. For the love, support, constant encouragement, and your persistent \textit{fighting}. I will love you always.

\pagebreak{}
