%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2016.  
%
%
%  Author: Sean Zachary Roberson
%	 Version 3.17.01 
%  Last updated 1/10/2017
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%             CONTRIBUTORS AND FUNDING SOURCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \chapter*{CONTRIBUTORS AND FUNDING SOURCES}
%% \addcontentsline{toc}{chapter}{CONTRIBUTORS AND FUNDING SOURCES}  % Needs to be set to part, so the TOC doesn't add 'CHAPTER ' prefix in the TOC.

%% \subsection*{Contributors}
%% This work was supported by a thesis (or) dissertation committee consisting of Professor XXXX [advisor --– also note if co-advisor] and XXX of the Department of [Home Department] and Professor(s) XXXX of the Department of [Outside Department].

%% The data analyzed for Chapter X was provided by Professor XXXX. The analyses depicted in Chapter X were conducted in part by Rebecca Jones of the Department of Biostatistics and were published in (year) in an article listed in the Biographical Sketch.

%% All other work conducted for the thesis (or) dissertation was completed by the student independently.
%% \subsection*{Funding Sources}
%% Graduate study was supported by a fellowship from Texas A\&M University and a dissertation research fellowship from XXX Foundation. 
%% \pagebreak{}

\chapter*{CONTRIBUTORS AND FUNDING SOURCES}
\addcontentsline{toc}{chapter}{CONTRIBUTORS AND FUNDING SOURCES}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

%% \noindent\textbf{Contributors}
\subsection*{Contributors}
This work was supervised by a dissertation committee consisting of Drs. Dindot [chair], Segal and Threadgill of the Department of Veterinary Pathobiology, and Dr. Burgess of the Department of Chemistry. Drs. Dindot and Threadgill have joint appointments in the Department of Molecular and Cellular Medicine.

The RNA-seq hybrid mouse data analyzed for Chapters 2 and 3 was generated by Wellcome Trust Sanger Institute, Genome Research Limited (reg no. 2742969) \url{http://www.sanger.ac.uk/science/data/mouse-genomes-project}. Several primers used in Chapters 2 and 3 were designed by Drs. Sarah Black Christian and Paul Hillman. The B6D2F1 female mouse tissues used in Chapters 2 and 3 were dissected and flash frozen by Dr. Ryan Doan. Primary neuronal cultures used in Chapter 3 were established by Ms. Hillary Shaheen. Ms. Jean Kovar maintained the mouse colonies. 

The image acquisition for high-throughput screening in Chapters 4 and 5 was conducted at Texas A\&M Institute of Biosciences \& Technology (IBT) in Houston, Texas. Dr. Clifford Stephan, Ms. Mary Sovieski, and Ms. Ivy Nuygen provided valuable technical support at the IBT. In addition, the Stephan group was in charge of changing media and adding drugs to the high-throughput data in Chapter 5.

The \textit{Ube3a$^{+/YFP}$} embryonic stem cells used in Chapter 5 were generated by TIGM (Texas A\&M Institute for Genomic Medicine). Additionally, neuronal differentiation scale increase for high-throughput screening by Dr. Johnathan Ballard at TIGM. 

All other work conducted for the dissertation was completed by the student independently.
%% \bigskip
%% \noindent\textbf{Funding}
\subsection*{Funding Sources}
Graduate study was supported by a Texas A\&M Institute for Genome Sciences and Society (formerly known as WSGI - Whole Systems Genomics initiative) fellowship and from Foundation for Angelman Syndrome Therapeutics (FAST).
\pagebreak{}
